---
title: "Planaria Regeneration and Patterning Lab Write-up"
subtitle: "Group 5, Reichard, Thursday 1:10-5:00 PM"
author:
  - Taylor Blair^[Reed College, tblair@reed.edu]
  - Morgan LeMay^[Reed College, manganft@reed.edu]
  - Connie Mangan^[Reed College, maxvanlan@reed.edu]
date: "`r format(Sys.time(), '%d %B, %Y')`"
lang: en-US
output:
  pdf_document:
    toc: true
    toc_depth: 3
    number_sections: true
urlcolor: blue
bibliography: "../bibliography.bib"
header-includes:
- \usepackage{booktabs}
- \usepackage{sectsty} \sectionfont{\centering}
abstract: "Is a pithy 8-10 sentences (100-250 words) to summarize your findings with enough relevant background so that any scientifically literate reader can understand your study. Every good abstract has some context/background, clearly states the question/hypothesis addressed, summarizes the results, and briefly discusses conclusions and/or implications of the results. (1/2 page). For more information, read the Bio Binder (Section T-3), and the writing abstracts handout for instructions and examples on how to craft an effective scientific abstract that includes background, results, and conclusions."
thanks: The authors are thankful to Katie Reichard for sheparding us...
---

\newpage

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = F, warning = FALSE, message = FALSE)
library(tidyverse)
library(kableExtra)
```



# Data

Data collected for the lab

```{r}
week_one <- read_csv("https://docs.google.com/spreadsheets/d/1Xwmnsy9RjIsFgfj2WjAcA4h1AzYWQaRr06DwQG8A9mI/gviz/tq?tqx=out:csv&sheet=data-collection")

week_one %>%
  kable()
```
 

Figure and Figure legend: Multi-panel figure that includes at least two plots of the data. The best figures will also include images of control and experimental planaria. Label the graph(s) and images sequentially with letters (ie: Panel A, Panel B). 
 
Statistical summary statements: At least two statistics summary statements that showcase the results from your (i) ANOVA or two-way ANOVA and (ii) chi-squared contingency analysis. See Bio Binder H-10 and H-12 for instructions and examples on how to write a summary statement, in addition to the relevant sections for ANOVA and chi-squared analyses for relevant numbers to report. 
 



\newpage

# Misc

Non write up section


## Author Contributions

> Contribution statement: See contribution statement guidelines and write who did what- Bio Binder T-10; Section U for a good example, Section V for a bad example.


All authors contributed equally to this project

## Grading

### Table

| **Component** | **Excellent** |	**Good**	| **Satisfactory**	| **Incomplete/Needs Work** | 
|---------------|---------------|-----------|-------------------|---------------------------|
|Report organization |          |           |                   |                           |
|Report organization |          |           |                   |                           |

### Other Comments

\newpage

# Bibliography